Correlation of filter methods

### 2021-04-05 analysis/filter-correlation.Rmd
wflow_publish(knitr_in("analysis/filter-correlation.Rmd"), view = FALSE, verbose = TRUE)
wflow_publish(knitr_in("analysis/filter-correlation.Rmd"), view = FALSE,     verbose = TRUE)

```{r filter-correlation-1, warning=FALSE}
fv_all_vi <- map(filter_values[8:14], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:89, 7)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_vi_fselecrcpp <- map(filter_values_fselectorrcpp[4:6], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:89, 3)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

@@

```{r correlation-filter-nri, dev = c("png", "pdf"), warning=FALSE}
fv_all_nri <- map(filter_values[15:21], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:7381, 7)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_nri_fselecrcpp <- map(filter_values_fselectorrcpp[7:9], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:7381, 3)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

@@

```{r filter-correlation-5, echo = FALSE}
system("sleep 5")
# file_move("docs/figure/filter-correlation.Rmd/correlation-nbins-1.pdf",
#           "code/98-paper/journal/")
# file_move("docs/figure/filter-correlation.Rmd/correlation-filter-nri-1.pdf",
#           "code/98-paper/journal/")
```

>>>>

```{r filter-correlation-1, warning=FALSE}
fv_all_vi <- map(filter_values[8:14], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:90, 7)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_vi_fselecrcpp <- map(filter_values_fselectorrcpp[4:6], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:90, 3)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

@@

```{r correlation-filter-nri, dev = c("png", "pdf"), warning=FALSE}
fv_all_nri <- map(filter_values[15:21], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:7875, 7)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_nri_fselecrcpp <- map(filter_values_fselectorrcpp[7:9], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:7875, 3)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

@@
